### 2023-12-08 paper/content.tex
Fix position of real data figure in preprint
Update references and remove footnote

@@

\begin{figure}[tb!]
\centering
\includegraphics[width=1\linewidth]{figures/real-data.png}
\caption{Real data and the various processing steps performed prior to the dipole moment inversion.
    a) The real sample vertical component magnetic data $b_z$ observations at
    $z = \qty{5}{\um}$.
    b) Anomaly map after the upward-continued data to $z = \qty{10}{\um}$ to attenuated long and short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the
    upward-continued data.
    d) The contrast-stretched TGA.
    e) The detected source bounding boxes (black squares) that correctly
    encapsulate the main signal of the sources.
    f) The estimated source locations (colored circles) from Euler
    Deconvolution of the upward-continued data inside each bounding box.
    The color represents the estimated $z$ coordinates.
  }
\label{real-data}
\end{figure}

@@

The Python source code used to produce all results and figures presented here, as well as supplemental figures and Jupyter notebooks, are available from \citet{sourcearchive}\footnote{Also avaliable on GitHub: \url{https://github.com/\GitHubRepository}} under the MIT and CC-BY licenses.
The QDM magnetic microscopy data are available
from \citet{janinedata} under the CC-0 license.

>>>>

\begin{figure}[ph!]
\centering
\includegraphics[width=1\linewidth]{figures/real-data.png}
\caption{Real data and the various processing steps performed prior to the dipole moment inversion.
    a) The real sample vertical component magnetic data $b_z$ observations at
    $z = \qty{5}{\um}$.
    b) Anomaly map after the upward-continued data to $z = \qty{10}{\um}$ to attenuated long and short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the
    upward-continued data.
    d) The contrast-stretched TGA.
    e) The detected source bounding boxes (black squares) that correctly
    encapsulate the main signal of the sources.
    f) The estimated source locations (colored circles) from Euler
    Deconvolution of the upward-continued data inside each bounding box.
    The color represents the estimated $z$ coordinates.
  }
\label{real-data}
\end{figure}

@@

@@

The Python source code used to produce all results and figures presented here, as well as supplemental figures and Jupyter notebooks, are available from \citet{sourcearchive}, also available on \url{https://github.com/\GitHubRepository} under the MIT and CC-BY licenses.
The QDM magnetic microscopy data are available
from \citet{janinedata} under the CC-0 license.
